---
title: 'R Shiny App: Global Happiness Index Distribution'
author: "Anne Strader"
date: "2023-05-01"
output: ioslides_presentation
---

<style>
pre {
  font-size: 14px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

- The objective of this Shiny app is to visualize the distribution of Happiness Index scores and rankings by country.
- Happiness index data for 2018 and 2019 are available.
- In addition to the overall happiness scores/rankings, the user can view scores from components used to calculate the happiness index:
    - GDP per capita
    - social support
    - healthy life expectancy
    - freedom to make life choices
    - generosity
    - perceptions of corruption

## Dataset

- The global happiness index dataset provides the following information:
    - country/region name
    - year for which happiness index was calculated (2018 or 2019)
    - happiness index ranking and score
    - scores of components used to calculate happiness score
    
```{r, load_data, echo = FALSE}
happiness.data <- read.csv("./Happiness-Index/data/report_2018-2019.csv", 
                           col.names = c("rank", "region", "year", 
                                         "score", "GDP", "social", "life", 
                                         "choices", "generosity", "corruption"))
```
    
```{r, show_data, echo = TRUE}
head(happiness.data)
```

## How to Use App

- Select score to display from the dropdown menu.
- Select year from which results will be displayed by clicking on the corresponding button.
- Select how many top-ranked countries for specified category and year to list by using the numeric input box.

## Links to App, Code

- The app can be found [here](https://anne-strader.shinyapps.io/Global-Happiness-Index/).
- All code is available at my [Github repository](https://github.com/seismostrader/Coursera-Developing-Data-Products-course-project).
